Geometric variational problems

### 2020-11-02 NSF2020/Description/background.tex
finished fixing up bibliography

Based on the physical origin of hydrophobicity,  we have devised a functional, called the hydrophobic attraction potential (HAP), to
model hydrophobic forces \cite{Fu19}. The motivation for HAP concept stemmed from the lead PI's 
earlier work on the problem of energy barriers in membrane fusion \cite{RyKlYaCo16,Chetal16}.
There, the lead PI and collaborators resolved the long-standing issue of accounting for the energy of a fissure surface
during topological transitions, by applying a squared gradient mathematical theory 
for hydrophobic attraction between planar surfaces \cite{Eriksson1989,Lum1999,Menshikov2017,Marcelja1977} to monolayer fissures.
Based on the PI Young's coarse-grained membrane modeling work \cite{Fu2017}, 
the investigators initiated a collaboration to create a gradient theory for arbitrary collections 
of hydrophobic and amphiphilic particles. This new method 
eliminates the costly calculation of water by treating the solvent implicitly, 
and avoids complicated re-meshing schemes of continuum approaches
by utilizing a particle-based representation.

@@

From a phenomenological perspective, (\ref{HAP}--\ref{SL}) 
is an appropriate model of hydrophobic attraction. Specifically,
using boundary layer analysis, it is possible 
to show that $\Phi$ converges to a surface energy in the zero-decay length limit \cite{Lee2018,Lin2015,Shibata2004}.
For non-zero decay lengths, solutions of \eqref{SL} yield an attractive interaction, e.g. between hydrophobic parallel disks
separated by water \cite{Eriksson1989}. Also, we have demonstrated with simulation that the forces 
derived from HAP theory are non-additive, and even deviate significantly from 
a pairwise potential \cite{Meyer2006,Fu19}. 
%The hydrophobic force has been implicated in the directed folding of proteins, 
%adhesion between biological membranes, but it is still unanswered as to whether
%the hydrophobic force of the form (\ref{HAP}--\ref{SL}) exists between small molecules.

@@

In our paper \cite{Fu19}, we developed the model (\ref{HAP}--\ref{SL})
to quantify the macroscopic assembly and mechanics of a lipid bilayer membrane in solvents. 
%We formulated the boundary value problem as a second-kind
%integral equation (SKIE), presented in the Section (). 
%The simulated fluid-particle systems exhibit a variety of multiscale behaviors over both time and length.
%Over short time scales, the numerical results showed self-assembly for model lipid particles. 
%For large system simulations, the particles formed realistic configurations like micelles and bilayers. 
%Our collections showed that these amphiphilic particle bilayers  possessed mechanical properties of a 
%lipid  bilayer  membrane  that  are  consistent  with other results in the literature.   
To define the particle dynamics, we considered the exterior domain $\Omega$
for a finite number of disjoint, rigid and closed particles $P_1$, $P_2$, \dots, $P_n$, each with Lipschitz boundary,
and boundary data $f$ in the Sobolev space $H^1(\Omega).$ 
For any fixed configuration, the functional \eqref{HAP} has a unique minimizer $u$
among all $u - f$ with vanishing trace. This minimizer is a solution to \eqref{SL}.
Conversely, from maximum principles and energy estimates,  any solution of 
\eqref{SL} is the minimizer of \eqref{HAP}, and this supplies $\Phi$ with a well-defined value.

@@

As a proof of concept, our work has already tested for elastic energies for bending, stretching and tilt of the bilayer assembly.
Extracting coefficients from the HAP simulations showed strikingly positive agreement with experimentally determined values  \cite{Fu19}.
Encouraged by these results and the hydrodynamic simulations of the bilayer assembly, the PIs propose to
further extend the HAP model and the numerical schemes (see \S\ref{sec:proposed-work})
to make direct comparison with experiments, the continuum liquid crystal results and MD simulations results, to establish that
the HAP model has the capability and adaptivity to model phenomena across length scales and time scales.
%
%
%The next few years provide the ideal window of opportunity for demonstrating the physical realism 
%of the HAP model. 
%
%
%
%The definitions and calculations for fully three-dimensional bilayer elastic energies are described in greater
%detail in Specific Aim 1. 
%

@@

%\section{Proposed Research}
%\label{sec:proposed-work}
%The goal of the proposed research is to develop fast,
%high-order-accurate, parallel numerical algorithms for large-scale
%simulations of the collective hydrodynamics of janus particles in a solvent in both two- and three-dimensions.
%First we summarize some basic formulation and preliminary results \cite{Fu19} in \S~\ref{subsec:bie} and \S~\ref{subsec:3dbie}.
%We then describe outstanding numerical issues that we propose to address  in \S~\ref{subsec:proposed_research}.

@@

%amphiphilic particles into two-dimensional micelles, bilayer membranes, and vesicles \cite{Fu19}.

@@

%the two-dimensional results in \cite{Fu19} are in agreement with the 

@@

%First we summarize some basic formulation and preliminary results \cite{Fu19} in \S~\ref{subsec:bie} and \S~\ref{subsec:3dbie}.

>>>>

Based on the physical origin of hydrophobicity,  we have devised a functional, called the hydrophobic attraction potential (HAP), to
model hydrophobic forces \cite{Fu2018_SIAM}. The motivation for HAP concept stemmed from the lead PI's 
earlier work on the problem of energy barriers in membrane fusion \cite{RyKlYaCo16,Chetal16}.
There, the lead PI and collaborators resolved the long-standing issue of accounting for the energy of a fissure surface
during topological transitions, by applying a squared gradient mathematical theory 
for hydrophobic attraction between planar surfaces \cite{Eriksson1989,Lum1999,Menshikov2017,Marcelja1977} to monolayer fissures.
Based on the PI Young's coarse-grained membrane modeling work \cite{Fu2017}, 
the investigators initiated a collaboration to create a gradient theory for arbitrary collections 
of hydrophobic and amphiphilic particles. This new method 
eliminates the costly calculation of water by treating the solvent implicitly, 
and avoids complicated re-meshing schemes of continuum approaches
by utilizing a particle-based representation.

@@

From a phenomenological perspective, (\ref{HAP}--\ref{SL}) 
is an appropriate model of hydrophobic attraction. Specifically,
using boundary layer analysis, it is possible 
to show that $\Phi$ converges to a surface energy in the zero-decay length limit \cite{Lee2018,Lin2015,Shibata2004}.
For non-zero decay lengths, solutions of \eqref{SL} yield an attractive interaction, e.g. between hydrophobic parallel disks
separated by water \cite{Eriksson1989}. Also, we have demonstrated with simulation that the forces 
derived from HAP theory are non-additive, and even deviate significantly from 
a pairwise potential \cite{Meyer2006,Fu2018_SIAM}. 
%The hydrophobic force has been implicated in the directed folding of proteins, 
%adhesion between biological membranes, but it is still unanswered as to whether
%the hydrophobic force of the form (\ref{HAP}--\ref{SL}) exists between small molecules.

@@

In our paper \cite{Fu2018_SIAM}, we developed the model (\ref{HAP}--\ref{SL})
to quantify the macroscopic assembly and mechanics of a lipid bilayer membrane in solvents. 
%We formulated the boundary value problem as a second-kind
%integral equation (SKIE), presented in the Section (). 
%The simulated fluid-particle systems exhibit a variety of multiscale behaviors over both time and length.
%Over short time scales, the numerical results showed self-assembly for model lipid particles. 
%For large system simulations, the particles formed realistic configurations like micelles and bilayers. 
%Our collections showed that these amphiphilic particle bilayers  possessed mechanical properties of a 
%lipid  bilayer  membrane  that  are  consistent  with other results in the literature.   
To define the particle dynamics, we considered the exterior domain $\Omega$
for a finite number of disjoint, rigid and closed particles $P_1$, $P_2$, \dots, $P_n$, each with Lipschitz boundary,
and boundary data $f$ in the Sobolev space $H^1(\Omega).$ 
For any fixed configuration, the functional \eqref{HAP} has a unique minimizer $u$
among all $u - f$ with vanishing trace. This minimizer is a solution to \eqref{SL}.
Conversely, from maximum principles and energy estimates,  any solution of 
\eqref{SL} is the minimizer of \eqref{HAP}, and this supplies $\Phi$ with a well-defined value.

@@

As a proof of concept, our work has already tested for elastic energies for bending, stretching and tilt of the bilayer assembly.
Extracting coefficients from the HAP simulations showed strikingly
positive agreement with experimentally determined values
\cite{Fu2018_SIAM}.
Encouraged by these results and the hydrodynamic simulations of the bilayer assembly, the PIs propose to
further extend the HAP model and the numerical schemes (see \S\ref{sec:proposed-work})
to make direct comparison with experiments, the continuum liquid crystal results and MD simulations results, to establish that
the HAP model has the capability and adaptivity to model phenomena across length scales and time scales.
%
%
%The next few years provide the ideal window of opportunity for demonstrating the physical realism 
%of the HAP model. 
%
%
%
%The definitions and calculations for fully three-dimensional bilayer elastic energies are described in greater
%detail in Specific Aim 1. 
%

@@

%\section{Proposed Research}
%\label{sec:proposed-work}
%The goal of the proposed research is to develop fast,
%high-order-accurate, parallel numerical algorithms for large-scale
%simulations of the collective hydrodynamics of janus particles in a solvent in both two- and three-dimensions.
%First we summarize some basic formulation and preliminary results
%\cite{Fu2018_SIAM} in \S~\ref{subsec:bie} and \S~\ref{subsec:3dbie}.
%We then describe outstanding numerical issues that we propose to address  in \S~\ref{subsec:proposed_research}.

@@

%amphiphilic particles into two-dimensional micelles, bilayer membranes,
%and vesicles \cite{Fu2018_SIAM}.

@@

%the two-dimensional results in \cite{Fu2018_SIAM} are in agreement with the 

@@

%First we summarize some basic formulation and preliminary results
%\cite{Fu2018_SIAM} in \S~\ref{subsec:bie} and \S~\ref{subsec:3dbie}.

### 2020-11-02 NSF2020/Description/broaderimpacts.tex
fixing up bibliography
finished fixing up bibliography

\noindent
{\it Broader impacts:} 
One PhD student (Szu-Pei Fu) was
funded to work with YNY, and work has resulted in seven papers
\cite{Nganguia2013_PoF,Nganguia2013_PRE,Young2014_JFM,Young2015_PoF,Nganguia2015_CiCP,Pak2015_PNAS,Fu2015_PRE}.
YNY has been actively involved with promotion of underrepresented students at NJIT. 
The other PhD student (Herve Nganguia) is African. YNY has taught a broad
spectrum of courses in fluid mechanics and applied math modeling.

@@

\noindent
{\it Broader impacts:} 
During the funded period, the PI has published or submitted twelve papers to refereed international journals~\cite{jiang2014sisc,bao2015jcp,jiang2015acom,greengard2015jcp,fu2015pre,gan2016sisc,jiang2016jcp,jiang2016oe,ben2016tpm,jiang2017siammms,jiang2017cicp,lai2018acha},
and presented the research results at many institutions and international
conferences/workshops to disseminate research results. On the education side,
the PI has supervised two students - Shaobo Wang~\cite{jiang2015acom,wang2019jsc}
and Szu-Pei Fu~\cite{fu2015pre,Fu19} (co-advised with Yuan-Nan Young),
with the partial support of the grant.
%Finally, the software package developed by both PIs of this collaborative grant
%has many applications in scientific computing, especially those related to
%the integral equation methods.

>>>>

\noindent
{\it Broader impacts:} 
One PhD student (Szu-Pei Fu) was
funded to work with YNY, and work has resulted in seven papers
\cite{Nganguia2013_PoF,Nganguia2013_PRE,Young2014_JFM,Young2015_PoF,Nganguia2015_CiCP,Pak2015_PNAS,fu2015pre}.
YNY has been actively involved with promotion of underrepresented students at NJIT. 
The other PhD student (Herve Nganguia) is African. YNY has taught a broad
spectrum of courses in fluid mechanics and applied math modeling.

@@

\noindent
{\it Broader impacts:} 
During the funded period, the PI has published or submitted twelve papers to refereed international journals~\cite{jiang2014sisc,bao2015jcp,jiang2015acom,greengard2015jcp,fu2015pre,gan2016sisc,jiang2016jcp,jiang2016oe,ben2016tpm,jiang2017siammms,jiang2017cicp,lai2018acha},
and presented the research results at many institutions and international
conferences/workshops to disseminate research results. On the education side,
the PI has supervised two students - Shaobo Wang~\cite{jiang2015acom,wang2019jsc}
and Szu-Pei Fu~\cite{fu2015pre,Fu2018_SIAM} (co-advised with Yuan-Nan Young),
with the partial support of the grant.
%Finally, the software package developed by both PIs of this collaborative grant
%has many applications in scientific computing, especially those related to
%the integral equation methods.

### 2020-11-02 NSF2020/Description/preliminarywork.tex
finished fixing up bibliography

In recent years, researchers have developed a number of numerical methods for calculating
energy minimizing steady equilibrium shapes of lipid bilayer membranes, vesicles and red blood cells.
These approaches range from the finite element method~\cite{Bartels,Peng13,RyKlYaCo16,Sinha15}, 
phase field method \cite{Du05,QiangDu08,Lowengrub13} to immersed boundary method  \cite{Hu,Hu13, Kim10}.
PI Ryham and collaborators led in part the development of phase field
functionals of membrane elastic energy and approaches to coupling membrane elasticity to fluids  \cite{0951-7715-18-3-016,Du05,DuEuler,QiangDu09}.

>>>>

In recent years, researchers have developed a number of numerical methods for calculating
energy minimizing steady equilibrium shapes of lipid bilayer membranes, vesicles and red blood cells.
These approaches range from the finite element method~\cite{Bartels,Peng13,RyKlYaCo16,Sinha15}, 
phase field method \cite{Du05,QiangDu08,Lowengrub13} to immersed
boundary method  \cite{Hu,Hu13, KimLai2010_JCP}.
PI Ryham and collaborators led in part the development of phase field
functionals of membrane elastic energy and approaches to coupling membrane elasticity to fluids  \cite{0951-7715-18-3-016,Du05,DuEuler,QiangDu09}.

### 2020-11-02 NSF2020/Description/specificaim1_ver2.tex
finished fixing up bibliography

\section{Proposed Research}
\label{sec:proposed-work}
The goal of the proposed research is to develop fast,
high-order-accurate, parallel numerical algorithms for large-scale
simulations of the collective hydrodynamics of  amphiphilic particles in a viscous solvent.
%
We have demonstrated that 
our potential theory approach can efficiently simulate self-assembly of 
amphiphilic particles into two-dimensional micelles, bilayer membranes, and vesicles \cite{Fu19}.
%
While these results show great potentials in simulating the collective hydrodynamics of amphiphilic particles and
reproducing mechanical properties of their bilayer assembly, 
several outstanding issues need to be addressed for such approach to be efficiently applied to three-dimensional 
collective hydrodynamics of amphiphilic particles.

@@

\subsubsection{Evidence for elastic properties}
\label{sssec:evidence}
We tested for elastic properties by subjecting two-dimensional bilayer morphologies
to external loads \cite{Fu19}, using realistic
values for phospholipid length \cite{Boal},
the screening length $\rho = 2.5$ nm \cite{Eriksson1989,Lin2005,Parsegian,Israelachvili80,TerziDeserno17}
and  interfacial tension $\gamma=4.1$ pN nm$^{-1}$  \cite{GarciaSaez, KUZMIN2005, Petelska2012}.
We first considered a planar bilayer subject to a uniform vertical load on the particle centers (Figure \ref{fig:bend}). 
The bilayer is clamped and horizontal at one end and the restoring force in the free part 
of the bilayer opposes the load. Twist and saddle splay are both zero, singling out splay
as the only distortion.
% In this situation, the directors are also parallel to the unit surface
%normal. As such $\Div \mathbf{d} = -2H$ where $H$ is the mean curvature of the surface. 
Since deformations are small \eqref{ansatz3}, it is possible to solve the bilayer loading in closed form. 
This analytical solution (red curve) basically overlaps the midplane of the particle based solution (Figure \ref{fig:bend}A).

\begin{wrapfigure}[13]{l}{0.5\textwidth}
\centerline{\includegraphics[width=0.5\textwidth]{figures/SA1_fig3.pdf}}
\caption{{\footnotesize (A) Energy barriers for stalk formation (i), hemifusion
diaphragm expansion (ii) and pore formation (iii). 
(B) Saddle-splay energy for each change in \emph{monolayer} topology
calculated in \cite{RyKlYaCo16}. (C)--(F): Shape transition of vesicle at different values of volume to area ratio from coarse-grained simulations of lipid bilayer membranes \cite{Fu16}.}}
\label{fig:barriers}
\end{wrapfigure}
Experimental measurements have accurately determined 
the bending modulus for several lipid types, with 
typical values lying around 10 \kBT\; \cite{Naetal15,VeBrPa15,NAGLE2000159,PhysRevLett.113.248102}.
By comparing with the exact solution, we derived a bending modulus
in the range 8.51 -- 13.54 \kBT, which is in 
excellent agreement with the experimentally derived value, especially considering how few parameters the HAP 
formalism involves.

We also considered the stretching deformation \cite{Fu19}. 
Stretching occurs whenever there is an excess monolayer area,
and it is energetically costly since it exposes hydrocarbon tails to water. 
%Monolayers are not, strictly speaking, area incompressible,
%and 
Manipulation experiments give a monolayer area modulus in the range 
30 -- 40 \kBT\; nm$^{-2}$ \cite{Nagle17, Nagle17-2}. 
To measure an area modulus, we stretched a circular vesicle, modeling the cross-section 
of a bilayer tube (Figure \ref{fig:bend}B \& C).
%We then stretched the vesicle beyond and beneath equilibrium radius and recorded the change in energy. 
This procedure gave a monolayer area modulus 
34 $\pm$ 2 \kBT \;nm$^{-2}$, independently of the vesicle size, which
is also remarkably close to the experimental value.

>>>>

\section{Proposed Research}
\label{sec:proposed-work}
The goal of the proposed research is to develop fast,
high-order-accurate, parallel numerical algorithms for large-scale
simulations of the collective hydrodynamics of  amphiphilic particles in a viscous solvent.
%
We have demonstrated that 
our potential theory approach can efficiently simulate self-assembly of 
amphiphilic particles into two-dimensional micelles, bilayer membranes,
and vesicles \cite{Fu2018_SIAM}.
%
While these results show great potentials in simulating the collective hydrodynamics of amphiphilic particles and
reproducing mechanical properties of their bilayer assembly, 
several outstanding issues need to be addressed for such approach to be efficiently applied to three-dimensional 
collective hydrodynamics of amphiphilic particles.

@@

\subsubsection{Evidence for elastic properties}
\label{sssec:evidence}
We tested for elastic properties by subjecting two-dimensional bilayer morphologies
to external loads \cite{Fu2018_SIAM}, using realistic
values for phospholipid length \cite{Boal},
the screening length $\rho = 2.5$ nm \cite{Eriksson1989,Lin2005,Parsegian,Israelachvili80,TerziDeserno17}
and  interfacial tension $\gamma=4.1$ pN nm$^{-1}$  \cite{GarciaSaez, KUZMIN2005, Petelska2012}.
We first considered a planar bilayer subject to a uniform vertical load on the particle centers (Figure \ref{fig:bend}). 
The bilayer is clamped and horizontal at one end and the restoring force in the free part 
of the bilayer opposes the load. Twist and saddle splay are both zero, singling out splay
as the only distortion.
% In this situation, the directors are also parallel to the unit surface
%normal. As such $\Div \mathbf{d} = -2H$ where $H$ is the mean curvature of the surface. 
Since deformations are small \eqref{ansatz3}, it is possible to solve the bilayer loading in closed form. 
This analytical solution (red curve) basically overlaps the midplane of the particle based solution (Figure \ref{fig:bend}A).

\begin{wrapfigure}[13]{l}{0.5\textwidth}
\centerline{\includegraphics[width=0.5\textwidth]{figures/SA1_fig3.pdf}}
\caption{{\footnotesize (A) Energy barriers for stalk formation (i), hemifusion
diaphragm expansion (ii) and pore formation (iii). 
(B) Saddle-splay energy for each change in \emph{monolayer} topology
calculated in \cite{RyKlYaCo16}. (C)--(F): Shape transition of vesicle
  at different values of volume to area ratio from coarse-grained
  simulations of lipid bilayer membranes \cite{Fu2017}.}}
\label{fig:barriers}
\end{wrapfigure}
Experimental measurements have accurately determined 
the bending modulus for several lipid types, with 
typical values lying around 10 \kBT\; \cite{Naetal15,VeBrPa15,NAGLE2000159,PhysRevLett.113.248102}.
By comparing with the exact solution, we derived a bending modulus
in the range 8.51 -- 13.54 \kBT, which is in 
excellent agreement with the experimentally derived value, especially considering how few parameters the HAP 
formalism involves.

We also considered the stretching deformation \cite{Fu2018_SIAM}. 
Stretching occurs whenever there is an excess monolayer area,
and it is energetically costly since it exposes hydrocarbon tails to water. 
%Monolayers are not, strictly speaking, area incompressible,
%and 
Manipulation experiments give a monolayer area modulus in the range 
30 -- 40 \kBT\; nm$^{-2}$ \cite{Nagle17, Nagle17-2}. 
To measure an area modulus, we stretched a circular vesicle, modeling the cross-section 
of a bilayer tube (Figure \ref{fig:bend}B \& C).
%We then stretched the vesicle beyond and beneath equilibrium radius and recorded the change in energy. 
This procedure gave a monolayer area modulus 
34 $\pm$ 2 \kBT \;nm$^{-2}$, independently of the vesicle size, which
is also remarkably close to the experimental value.

### 2020-11-02 NSF2020/Description/specificaim2_ver2.tex
fixing up bibliography
finished fixing up bibliography

The discretization of the integral operator often leads to a dense matrix,
while finite difference/finite element methods result in sparse matrices,
making matrix-vector product much cheaper to compute. However,since the invention
of the original fast multipole method (FMM)\cite{fmm5}, there
have been many fast algorithms~\cite{fmm1,fmm2,fmm3,fmm4,fmm6,fmm7,fmm8}
that reduce the cost of matrix-vector product
to linear ($O(N)$) or quasilinear complexity ($O(N \log^kN)$) for dense matrices resulting
from the BIE discretization.
Fast direct solvers have also been developed
recently~\cite{fds1,fds2,fds3,fds4,fds5,fds6,fds7,fds8,ho2016cpam2,ho2016cpam1,minden2016,minden2017siammms}.
The development of these fast algorithms have removed a huge
hurdle for the use of boundary integral equations, making the BIE method the method
of choice for constant-coefficient PDEs with linear boundary conditions. For the exterior
Dirichlet problem of the screened Laplace equation, the SKIE formulation in our previous
work~\cite{Fu19} can be readily extened to the 3D case. For the mobility problem
of the Stokes flow in three dimensions that
takes the hydrodynamic effect into account, an SKIE formulation
can be found in \cite{manasthesis}.

@@

In practice, there are still many issues that need to be resolved.
For example, there are now many variants of QBX including global and local
QBX~\cite{klockner2013jcp,rachh2017jcp}, the target-specific QBX~\cite{siegel2018jcp},
kernel-independent QBX~\cite{abtin2018bit}, and
quadrature by two expansions~\cite{ding2019arxiv}. The coupling of the QBX
and the FMM may also lead to certain instability issues which may require
some changes in the fast multipole method~\cite{wala2018jcp}. Similar
to other quadrature methods, there have been extensive study on the QBX
methods in two dimensions, while its three dimension
version~\cite{wala2019jcp,af2018sisc,siegel2018jcp,wala2019arxiv} has not been
fully studied and the implementation is even more scarce. We plan to investigate
the accuracy and the convergence order of the various QBX schemes mentioned above,
its coupling with the FMM, parallel implementation issues for large-scale
problems, and the application to our target problems.
\subsubsection{A hybrid method for close-to-touching Janus particles}
The HAP model for membranes will inevitably lead to the case where some Janus particles
will be very close to each other. Even though QBX can handle such case
accurately, it may lead to excessively large number of unknowns in order to resolve
the unknown densities at those close-to-touching points. In \cite{gan2016sisc},
a hybrid scheme is developed to treat the close-to-touching spheres for the interface
problem of the Laplace equation. The key idea is to combine the analytic image method
and spectrally accurate method of moments, where the analytic image method will capture
the most singular part of the unknown density at the close-to-touching points.
With the aid of the FMM, the scheme achieves linear complexity with much less number
of unknowns on the material interfaces.
We plan to study the hybrid scheme
to treat the close-to-touching case for both the screened Laplace equation and the
mobility problem to further improve the efficiency of the numerical algorithm
for the HAP model.
\subsubsection{Other numerical issues}
Another outstanding numerical issue pertaining to simulating the self-assembly of amphiphilic particles (such as lipid macromolecles) in a
viscous solvent is the collision between amphiphilic particles.
The hydrophobic attraction potential drives the amphiphilic particles to move towards each other so to minimize exposure to the solvent. 
Under such
attraction force the fluid is being squeezed out as particles move toward each other, and the amphiphilic particles can come into physical
contact in finite time. 
Such particle collisions in a dense rigid body suspension is a great challenge and can be a bottleneck in large-scale simulations. 
In our previous work a Leonard-Jones potential is used to keep the particles from overlapping \cite{Fu19}. 
Such steep steric interaction at
short ranges introduces great numerical stiffness that limit the time step size.

@@

Once the collision-resolution algorithm is implemented, we will check the computing performance first before we embark on 
incorporating fluctuating hydrodynamics \cite{Bao17,Bao18}, which might be important even at the scales of the amphiphilic 
particle size in some cases. We propose to extend the high-order time-integration scheme for a stochastic differential equation \cite{Fu15} to
this system.

>>>>

The discretization of the integral operator often leads to a dense matrix,
while finite difference/finite element methods result in sparse matrices,
making matrix-vector product much cheaper to compute. However,since the invention
of the original fast multipole method (FMM)\cite{fmm5}, there
have been many fast algorithms~\cite{fmm1,fmm2,fmm3,fmm4,fmm6,fmm7,fmm8}
that reduce the cost of matrix-vector product
to linear ($O(N)$) or quasilinear complexity ($O(N \log^kN)$) for dense matrices resulting
from the BIE discretization.
Fast direct solvers have also been developed
recently~\cite{fds1,fds2,fds3,fds4,fds5,fds6,fds7,fds8,ho2016cpam2,ho2016cpam1,minden2016,minden2017siammms}.
The development of these fast algorithms have removed a huge
hurdle for the use of boundary integral equations, making the BIE method the method
of choice for constant-coefficient PDEs with linear boundary conditions. For the exterior
Dirichlet problem of the screened Laplace equation, the SKIE formulation in our previous
work~\cite{Fu2018_SIAM} can be readily extened to the 3D case. For the mobility problem
of the Stokes flow in three dimensions that
takes the hydrodynamic effect into account, an SKIE formulation
can be found in \cite{manasthesis}.

@@

In practice, there are still many issues that need to be resolved.
For example, there are now many variants of QBX including global and local
QBX~\cite{klockner2013jcp,rachh2017jcp}, the target-specific QBX~\cite{siegel2018jcp},
kernel-independent QBX~\cite{abtin2018bit}, and
quadrature by two expansions~\cite{ding2019arxiv}. The coupling of the QBX
and the FMM may also lead to certain instability issues which may require
some changes in the fast multipole method~\cite{wala2018jcp}. Similar
to other quadrature methods, there have been extensive study on the QBX
methods in two dimensions, while its three dimension
version~\cite{wala2019jcp,af2018sisc,siegel2018jcp,wala2019arxiv} has not been
fully studied and the implementation is even more scarce. We plan to investigate
the accuracy and the convergence order of the various QBX schemes mentioned above,
its coupling with the FMM, parallel implementation issues for large-scale
problems, and the application to our target problems.
\subsubsection{A hybrid method for close-to-touching Janus particles}
The HAP model for membranes will inevitably lead to the case where some Janus particles
will be very close to each other. Even though QBX can handle such case
accurately, it may lead to excessively large number of unknowns in order to resolve
the unknown densities at those close-to-touching points. In \cite{gan2016sisc},
a hybrid scheme is developed to treat the close-to-touching spheres for the interface
problem of the Laplace equation. The key idea is to combine the analytic image method
and spectrally accurate method of moments, where the analytic image method will capture
the most singular part of the unknown density at the close-to-touching points.
With the aid of the FMM, the scheme achieves linear complexity with much less number
of unknowns on the material interfaces.
We plan to study the hybrid scheme
to treat the close-to-touching case for both the screened Laplace equation and the
mobility problem to further improve the efficiency of the numerical algorithm
for the HAP model.
\subsubsection{Other numerical issues}
Another outstanding numerical issue pertaining to simulating the self-assembly of amphiphilic particles (such as lipid macromolecles) in a
viscous solvent is the collision between amphiphilic particles.
The hydrophobic attraction potential drives the amphiphilic particles to move towards each other so to minimize exposure to the solvent. 
Under such
attraction force the fluid is being squeezed out as particles move toward each other, and the amphiphilic particles can come into physical
contact in finite time. 
Such particle collisions in a dense rigid body suspension is a great challenge and can be a bottleneck in large-scale simulations. 
In our previous work a Leonard-Jones potential is used to keep the
particles from overlapping \cite{Fu2018_SIAM}. 
Such steep steric interaction at
short ranges introduces great numerical stiffness that limit the time step size.

@@

Once the collision-resolution algorithm is implemented, we will check the computing performance first before we embark on 
incorporating fluctuating hydrodynamics \cite{Bao17,Bao18}, which might be important even at the scales of the amphiphilic 
particle size in some cases. We propose to extend the high-order
time-integration scheme for a stochastic differential equation
\cite{fu2015pre} to
this system.
